\documentclass[12pt]{article}

\input{settings/settings.tex}

\title{Article review for Patrik Högblom (pahg1600)}
\author{Linus Sjöbro}
\date{\today}

\begin{document}
\maketitle

\section{Overall} \label{}
The title feels a little bit ''framed in'' when it's constructed as ''...of two different... '' and ''... on a cheap...''. Maybe reform it into something like \textit{Performance evaluation in different graph drawing libraries on cheap IoT devices} would be better.

\bigskip

All the text in the article is in bold. Only the abstract section should be all bold.

\bigskip

The information in the header is on Swedish which it shouldn't be. Change this to english instead.

\bigskip

You should also read through the whole article to correct and change sentences that sounds lumpish and that's grammatically wrong.

\section{Abstract} \label{}
The purpose part of the abstraction confuses me. The title states that different graph drawing libraries will be tested. But the purpose states that graph libraries will be tested, but also to ''make a webserver''. Which acts like a personal cloud. 

\section{Introduction} \label{}
The sentence \textit{''Also, another risk is that company employees may steal the user’s information through only logging in on the server''} just before the last paragraph of the Introduction feels a bit off. I doubt these large cloud providers doesn't use better security than that. So to state that it's that easy for employees to access costumers personal data feels misleading.

\bigskip

The purpose stills confuse me after I have read through the introduction. What part does the webserver has in this project? I thing this should be more explained in the introduction. More than the current explanation which is \textit{''...One of the solutions is to have a personal cloud''}.

\bigskip

Other than that the introduction is not much to complain about.

\section{Related work} \label{}
This part is very short and not very explaining. The purpose with the related work is to get a brief insight into other researches that has been done in this area. Right now it doesn't really say that much. Also the sentence withe reference [6] and [7] (The last sentence) does not belong here.

\section{Research question and hypothesis} \label{}
Now it's clear why you also going to use/need a webserver.Your abstract should (shortly) explain why you need a webserver. Up to this point i couldn't figure out why you need a webserver.

Also the goal and purpose is kind of the same thing. So I think you could remove the purpose part of the introduction and just run with the goal.

\section{method} \label{}
Almost the whole method could be removed. It's not in the readers interest to read what peripheral your using and how you install the different libraries etc. This also include \textit{Figure 1}.

\bigskip

The method should more explain why your doing in a certain way. The last paragraph of the method describes how your doing to get your result. So I would rewrite the method to something like this last paragraph to explain how your doing things in detail. For example, how does the libraries work? How does it process data etc.

\section{Result} \label{}
Tables needs numbering. Use the \LaTeX-way to do this.

\bigskip

What information does the tables present? The first table for example. The first sample. What is $115$? Seconds? Minutes? Hours? Specify what kind of data that being presented.

\bigskip

The result is also a bit messy and hard to follow. Look how you could present it in a better way.

\section{References} \label{}
Look how the \LaTeX-reference system works and use that instead of an own alternative that's not mainstream and different across all references.
\end{document}